Data Predictive Control with Random Forests:\\Theory and Applications\tnoteref{mytitlenote}

### 2017-09-29 paper/casestudyReal.tex
small edits

In this section we show an application of DPC to a real case study. The section organization is shown in Figure \ref{F:overview}. More precisely, we consider a real house located in L'Aquila, Italy, as a case study that we describe in Section \ref{SS:descriptionHouse}. Using historical data from this house, random forest models are built in Section \ref{SS:randomForestsModels} to be used either as plant or as predictive models for DPC. In Section \ref{SS:controllersDPCandBangbang}, DPC and bang-bang control strategies are defined to be used in the close-loop simulations. Finally in Section \ref{SS:simulationResults} controllers performance are compared in terms of energy saving using a thermal energy model of the house built via EnergyPlus in Section \ref{SS:energyPlusmodel}, using both historical data, and house construction layout and materials.

\begin{figure}[h!]
	\begin{center}
		\includegraphics[width=1\linewidth]{figures/overview.eps}
		\caption{Section \ref{S:realCaseStudy} organization scheme.}
		\captionsetup{justification=centering}
		\label{F:overview}
	\end{center}
\end{figure}

>>>>

In this section, we show an application of DPC to a real house located in L'Aquila, Italy. Random forest models for DPC built using historical data from this house are described in Section \ref{SS:randomForestsModels}. 
In Section \ref{SS:energyPlusmodel}, we present the thermal energy model of the building in EnergyPlus, built using historical data, construction layout and materials after spending $\sim3$ months of efforts.
In Section \ref{SS:controllersDPCandBangbang}, we set up the DPC optimization problem and describe the bang-bang control strategy. Finally, in Section \ref{SS:simulationResults}, the performance of the two controllers are compared in terms of energy saving using the EnergyPlus model. The section organization is graphically shown in Figure \ref{F:overview}.

\begin{figure}[h!]
	\begin{center}
		\includegraphics[width=1\linewidth]{figures/overview.eps}
		\caption{Random Forest trained on all features including the control variable are used as the plant in the closed-loop simulations with DPC and bang-bang controller. DPC optimzation uses Random Forests with affine functions as predictive models. Controllers' strategies are evaluated using the EnergyPlus model to compare the actual energy consumption.}
		\captionsetup{justification=centering}
		\label{F:overview}
	\end{center}
\end{figure}

### 2017-09-29 paper/intro.tex
small edits

\paragraph{Example} As an example of such modeling complexity, consider the grey-box approach in \cite{Braun2002}. The scope of such approach is to predict the heat transfer rate to the air within the building. In particular, the authors addressed a single zone modeling problem using an equivalent $RC$ model. To this aim, five different types of structures are considered in the example: external walls, ceiling/roof, floor, internal walls and windows. Each of these elements are represented using $3$ resistances, $2$ capacitances and $2$ temperatures, except for the windows that are represented only with resistances since they have a negligible energy storage. A model consisting of $8$ states and $9$ inputs, including disturbances such as solar radiation and others, with the instantaneous heat gain to the building air from all surfaces as output, is created for the zone. To have a complete LTI model, $9$ parameters needed to be estimated through a non-trivial training process, using a collection of information associated with a physical description of the building (see \cite{Braun2002} for more details). In Section \ref{S:realCaseStudy} we will consider an application of the methodology proposed in this paper on a real house with $10$ different zones. This means that, in order to have a model of the zones as the one just described, only for what concerns the heat transfer rate within the building, and hence neglecting the energy consumption model of the house, we would need to consider a model with around $80$ states and $90$ parameters to be estimated.

>>>>

\paragraph{Example} As an example of such modeling complexity, consider the grey-box approach in \cite{Braun2002}. The scope of such approach is to predict the heat transfer rate to the air within the building. In particular, the authors addressed a single zone modeling problem using an equivalent $RC$ model. To this end, five different types of structures are considered in the example: external walls, ceiling/roof, floor, internal walls and windows. Each of these elements are represented using $3$ resistances, $2$ capacitances and $2$ temperatures, except for the windows that are represented only with resistances since they have a negligible energy storage. A model consisting of $8$ states and $9$ inputs, including disturbances such as solar radiation and others, with the instantaneous heat gain to the building air from all surfaces as output, is created for the zone. To have a complete LTI model, $9$ parameters are needed to be estimated via a non-trivial training process, using a collection of information associated with a physical description of the building (see \cite{Braun2002} for more details). Extending this result, for the building we consider in Section \ref{S:realCaseStudy} with $10$ different zones, we would need to consider a model with approximately $80$ states and $90$ parameters to be estimated.
